disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-22 article.Rnw
Correct typo in table

%
\begin{table}
\centering
\begin{tabular}{l|ll|ll}
 & \multicolumn{2}{|c|}{MCMC (94 hours)} & \multicolumn{2}{|c}{TMB (56 seconds)} \\
Parameter & Mean & SD & Mean & SD \\
\hline
Intercept & -3.09 & 0.33 & -3.12 & 0.27 \\
Slope 1 & 0.20 & 0.28 & 0.24 & 0.27 \\
Slope 2 & 0.32 & 0.21 & 0.30 & 0.21\\
Slope 3 & -0.36 & 0.20 & -0.37 & 0.20 \\
Slope 4 & -0.24 & 0.23 & -0.24 & 0.21 \\
iid $log(\tau)$ & 1.08 & 0.27 & 1.10 & 0.27 \\
$log(\sigma)$ & -3.34 & 0.59 & -3.55 & 0.59 \\
$log(\rho)$ & 0.72 & 0.31 & -0.56 & 0.30 \\
\end{tabular}
\caption{Fitted model parameter values using both MCMC and using \pkg{TMB} within the \pkg{disaggregation} package.}
\label{tab:mcmcresults}
\end{table}
%

>>>>

%
\begin{table}
\centering
\begin{tabular}{l|ll|ll}
 & \multicolumn{2}{|c|}{MCMC (94 hours)} & \multicolumn{2}{|c}{TMB (56 seconds)} \\
Parameter & Mean & SD & Mean & SD \\
\hline
Intercept & -3.09 & 0.33 & -3.12 & 0.27 \\
Slope 1 & 0.20 & 0.28 & 0.24 & 0.27 \\
Slope 2 & 0.32 & 0.21 & 0.30 & 0.21\\
Slope 3 & -0.36 & 0.20 & -0.37 & 0.20 \\
Slope 4 & -0.24 & 0.23 & -0.24 & 0.21 \\
iid $log(\tau)$ & 1.08 & 0.27 & 1.10 & 0.27 \\
$log(\sigma)$ & -3.34 & 0.59 & -3.55 & 0.59 \\
$log(\rho)$ & 0.72 & 0.31 & 0.56 & 0.30 \\
\end{tabular}
\caption{Fitted model parameter values using both MCMC and using \pkg{TMB} within the \pkg{disaggregation} package.}
\label{tab:mcmcresults}
\end{table}
%
